---
title: "ESPN Scrape"
author: "Joe Jenkins"
date: "9/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I scrapped 7 games from ESPN and the 2020 NBA playoffs. The link that this code is based on is the following:

  - https://www.espn.com/nba/schedule/_/date/20200910
  
### Packages Used

```{r}
library(httr)
library(rvest)
library(stringr)
library(DT)
link <- "https://www.espn.com/nba/schedule/_/date/20200910"
```

### Scrapping the Initial Page
First, I scrapped the homepage to get all of the unique game ids.

```{r}
nba <- read_html(link)
nba_links <- nba%>% 
  html_nodes("a[href*='/nba/game?gameId=']") %>% 
  html_attr("href") %>% 
  unique() %>% 
  str_replace(., "/nba/game", "") %>% 
  paste("https://www.espn.com/nba/playbyplay", ., sep ="")
```

### Creating a Function to Get the Games
Next, I created a function to get the games so I did not have to individually call for each game. Then I executed the function and saved it to object "games"

```{r}
get_games <- function(x) {
  read_html(x) %>% 
    html_table(fill = TRUE)
}

games <- lapply(nba_links, get_games)
```

### Combining Quarters Function 
After this, I created two functions. One called, "combine_quarters_1" and the other called "combine_quarters_2." Some of the calls have two dataframes along with the ones we want and some have only one extra data frame. Due to this, I created two functions and called them appropriately. In addition, it drops two columns that only cotain the value NA. Finally, if I was doing any sort of work with this data, I would have added the quarter to the data frame. However, in my opnion this is a data scraping exercise and thus that was outside the scope of this project.

```{r}
combine_quarters_1 <- function(x) {
  table_length <- length(x) - 1
  datalist <- list()
  for (y in 2:table_length) {
    iteration <- y - 1
    datalist[[iteration]] <- x[[y]]
  }
  out <- do.call(rbind, datalist)
  out <- out[,c(1,3,4)]
}

combine_quarters_2 <- function(x) {
  table_length <- length(x) - 2
  datalist <- list()
  for (y in 2:table_length) {
    iteration <- y - 1
    datalist[[iteration]] <- x[[y]]
  }
  out <- do.call(rbind, datalist)
  out <- out[,c(1,3,4)]
}
```

### Creating Data Frames
Next, I called the appropriate function and named each game correctly based on the teams playing.

#### Los Angles Lakers vs. Houston 

```{r}
LAL_HOU <- games[[1]]
LAL_HOU <- combine_quarters_2(LAL_HOU)
```

#### Denver vs. Los Angeles Clippers

```{r}
DEN_LAC <- games[[2]]
DEN_LAC <- combine_quarters_2(DEN_LAC)
```

#### Boston vs. Toronto 

```{r}
BOS_TOR <- games[[3]]
BOS_TOR <- combine_quarters_1(BOS_TOR)
```

#### Houston vs. Los Angeles Lakers

```{r}
HOU_LAL <- games[[4]]
HOU_LAL <- combine_quarters_2(HOU_LAL)
```

#### Los Angeles Clippers vs. Denver 

```{r}
LAC_DEN <- games[[5]]
LAC_DEN <- combine_quarters_2(LAC_DEN)
```

#### Miami vs. Boston 

```{r}
MIA_BOS <- games[[6]]
MIA_BOS <- combine_quarters_2(MIA_BOS)
```

#### Denver vs. Los Angeles Clippers

```{r}
DEN_LAC <- games[[7]]
DEN_LAC <- combine_quarters_2(DEN_LAC)
```

#### Printing the DataFrames 

#### Los Angles Lakers vs. Houston 

```{r}
DT::datatable(LAL_HOU)
```

#### Denver vs. Los Angeles Clippers

```{r}
DT::datatable(DEN_LAC)
```

#### Boston vs. Toronto 

```{r}
DT::datatable(BOS_TOR)
```

#### Houston vs. Los Angeles Lakers

```{r}
DT::datatable(HOU_LAL)
```

#### Los Angeles Clippers vs. Denver 

```{r}
DT::datatable(LAC_DEN)
```

#### Miami vs. Boston 

```{r}
DT::datatable(MIA_BOS)
```

#### Denver vs. Los Angeles Clippers

```{r}
DT::datatable(DEN_LAC)
```